---
title: "Include Code Files"
author: Shafayet Khan Shafee
date: last-modified
format:
  html: 
    code-fold: true
engine: knitr
filters:
  - include-code-files
execute: 
  echo: true
---


> Note that, If you are rendering the quarto document using jupyter use {python} chunk to include code and on the other hand if you are rendering the quarto document using knitr (i.e. engine: knitr) then use {r} chunk to include code, Or to avoid thinking about rendering engine, jupyter or knitr, you also can follow pandoc Div approach described below.


## `add-code-from`

You can include code from a file using `add-code-from` chunk option. And while using knitr for rendering the quarto document, use `r` chunk, even though you are adding contents of different language other than R and to enable syntax highlighting correctly, use chunk option `source-lang`. (You can run `quarto pandoc --list-highlight-languages` to know for which languages, syntax highlighting is supported and use one of those in `source-lang` accordingly)

```{r}
#| add-code-from: test/snippets/capitalize.m
#| source-lang: matlab

# comment
```

**One very important detail to note that, you must put a random comment in code chunk so that the code chunk is not treated as empty, to make this filter work.**

## `start-line` & `end-line`

You can specify from which line to which line you want to include,


```{r}
#| add-code-from: test/snippets/capitalize.ts
#| source-lang: typescript
#| start-line: 1
#| end-line: 4
#| code-line-numbers: true

# comment
```

Note that, we have used `code-line-numbers: true` to add line numbers in code chunk.

## `dedent`

You can specify a line number for which whitespaces will be removed using the `dedent` option.


## Don't want to use `source-lang`

If you **do not** want to use `r` chunk (i.e. ````{r}`) to include content from files and **do not** want to use `source-lang` option also, you can do the following,

::: {add-code-from=test/snippets/capitalize.php start-line=1 end-line=17 code-line-numbers="true"}

```{.php}
```

:::

Here we have defined all the chunk option for a pandoc div (i.e. `:::`) and used a php chunk to add code from `capitalize.php`.


## filename

We can use `filename` either within a r chunk or in pandoc div with `add-code-from` attribute to include a code filename.


```{r}
#| add-code-from: test/snippets/fizz-buzz.rs
#| source-lang: rust
#| code-line-numbers: true
#| filename: fizz-buzz.rs

# comment
```


::: {add-code-from=test/snippets/fizz-buzz.jl code-line-numbers="true" filename=fizz-buzz.jl}

```{.julia}
```

:::


**Note that, `code-fold`-ing does not work when a filename is specified.**
